Finiteness in Cubical Type Theory

### 2020-05-07 paper.tex
updated to acm format

\input{preamble}
\title{Finiteness in Cubical Type Theory}
\author{
  Donnacha Oisín Kidney\inst{1}\and Gregory Provan \inst{2}
}
\institute{
  University College Cork \email{o.kidney@cs.ucc.ie} \and
  University College Cork \email{g.provan@cs.ucc.ie}
}
\begin{document}
\maketitle
\begin{abstract}
  We study five different notions of finiteness in Cubical Type Theory and prove
  the relationship between them.
  In particular we show that any totally ordered Kuratowski finite type is
  manifestly Bishop finite.

@@

  We formalise our work in Cubical Agda, where we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying).
  Through this library we demonstrate a number of uses for the computational
  content of the univalence axiom, including searching for and synthesising
  functions.
  \keywords{Agda \and Homotopy Type Theory \and Cubical Type Theory \and
    Dependent Types \and Finiteness \and Topos \and Kuratowski finite}
\end{abstract}
\section{Introduction}
\subsection{Foreword}
In constructive mathematics we are often preoccupied with \emph{why} something
is true.
Take finiteness, for example.
There are a handful of ways to demonstrate some type is finite: we could provide
a surjection to it from another finite type; we could show that any collection
of its elements larger than some bound contains duplicates; or we could show
that any stream of its elements contain duplicates.

@@

\cite{iversenUnivalentCategoriesFormalization2018} provided a starting point for
our categorical formalisation: it contains a proof, for instance, that homotopy
sets form a category.

\subsubsection*{Acknowledgement}
This work has been supported by the Science Foundation Ireland under the
following grant: 13/RC/2D94 to Irish Software Research Centre.
\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
\end{document}

>>>>

\input{preamble}
\acmConference[TyDe 2020]{Workshop on Type-driven Development}{23 Aug
  2020}{Jersey City, USA}

\author{Donnacha Oisín Kidney}
\affiliation{University College Cork}
\email{o.kidney@cs.ucc.ie}
\author{Gregory Provan}
\affiliation{University College Cork}
\email{g.provan@cs.ucc.ie}
\author{Nicolas Wu}
\affiliation{Imperial College London}
\email{n.wu@imperial.ac.uk}

\title{Finiteness in Cubical Type Theory}

\keywords{Agda, Homotopy Type Theory, Cubical Type Theory,
  Dependent Types, Finiteness, Topos, Kuratowski finite}

\begin{abstract}
  We study five different notions of finiteness in Cubical Type Theory and prove
  the relationship between them.
  In particular we show that any totally ordered Kuratowski finite type is
  manifestly Bishop finite.

@@

  We formalise our work in Cubical Agda, where we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying).
  Through this library we demonstrate a number of uses for the computational
  content of the univalence axiom, including searching for and synthesising
  functions.
\end{abstract}

\begin{document}
\maketitle
\section{Introduction}
\subsection{Foreword}
In constructive mathematics we are often preoccupied with \emph{why} something
is true.
Take finiteness, for example.
There are a handful of ways to demonstrate some type is finite: we could provide
a surjection to it from another finite type; we could show that any collection
of its elements larger than some bound contains duplicates; or we could show
that any stream of its elements contain duplicates.

@@

\cite{iversenUnivalentCategoriesFormalization2018} provided a starting point for
our categorical formalisation: it contains a proof, for instance, that homotopy
sets form a category.
\begin{acks}
  This work has been supported by the Science Foundation Ireland under the
  following grant: 13/RC/2D94 to Irish Software Research Centre.
\end{acks}
\printbibliography
\end{document}
